Stack Safety as a Security Property

### 2020-07-01 main.tex
Minor (maybe just spacing)

But what {\em is} stack safety? A precise formal definition of stack
safety is lacking from the literature, with the notion only being
defined negatively: through examples of stack unsafety
\rb{usually though not always; as noted below there are other approaches}. Two classical
examples of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad write.}
\leo{Do we also need an example of ROP/control flow for the new part?}
Recently, a \leo{inspiring/awesome/something good} work reasoned
about a stack safety enforcement mechanism using capabilities\leo{cite};
while impressive, stack safety was defined with respect to an abstract
machine that ``exhibits stack safety by construction''. Which begs
the question, what {\em is} the property that holds by construction?

\leo{StackTokens} provides some intuition towards answering that question,
by informally describing two components that comprise stack safety:
local state encapsulation and well-bracketed control flow. In this paper
we turn this intuition into two formal \leo{extensional} security properties,
that together form a formal definition of stack safety.
\rb{I think the merit of StkTokens goes beyond mere intuition. There is a lot of
rigor in it, even if some notions are implicit or not fully developed.}

@@

While integrity and confidentiality are relatively standard security
properties, this setting provides an interesting additional challenge:
the notion of who the attacker is shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be potentially proteced from {\em its} callees.  In
this paper we address this challenge by varying the observation power
of the attacker at call points, and demonstrate that our policy is
implementable by pre-existing monitoring mechanisms.

@@

Before we define stack safety, we need to first set the stage by
describing our machine model. Concretely, we have in mind a
conventional machine architecture with a standard (RISC-V) processor
extended with some kind of (static or dynamic, software- or
hardware-enforced) security monitor
\rb{Put stress on genericity first, advance this concrete model after?}.
However, our definition of stack
safety is generic: we will begin with an abstract interface to our
machine model and only make specific choices about details when we get
to the policy enforcement section~\ref{sec:micropolicy}.

@@

The basic building blocks of the machine are {\em values} and {\em
  addresses}. Both are drawn from some set of all possible words
$\WORDS$. We will denote words with $\word$.
%
Our machine states are comprised of {\em components}, that can be word
(denoting memory addresses) or registers (drawn from some set $\REGS$).
%
    \[\reg \in \REGS\]
    \[\component \in \COMPONENTS = \WORDS + \REGS \]
%
The registers must include two special purpose registers: the program
counter {\PCname} and the stack pointer \SP.
%
Formally, a machine state is just a map from components to values:
%
\[\mach \in \MACHS = \COMPONENTS \rightarrow \WORDS\]

@@

A trace over some type $A$ is a potentially infinite, nonempty
sequence of $A$s. We will mostly be concerned with sequences of
machines states, usually denoted $\machT$, and with sequences of
triples of (machine states, policy states, and observations), usually
denoted $\MPT$.
\rb{The way the definitions are set up, one may expect MPO, but\ldots}
To continue, we will require three \rb{four?} generic operations
on traces: a ``trace-of'' operation to construct the potentially
infinite traced induced by a step relation
\rb{not an op on traces per se?};
a ``split'', to break a
trace into two components based on a predicate; a ``join'', the
reverse of split; and a ``prefix'', as a shorthand to only keep the
first component of a split.

@@

\subsection{Program Structure}

@@

\definition{Trace Integrity}
\label{def:trace-integrity}

Let $\contour$ be a contour and $MP$ be a (potentially infinite)
$\MPOTRACE$. We will say $MP$ satisfies {\em trace integrity} with
respect to $\contour$ if its final state (if any) agrees with its
initial one on all components marked $\HIGHSEC$ in $\contour$:
%
\[
\mathit{int} ~ \contour ~ MP \triangleq
\left \{ \begin{array}{ll}
  \mathit{True}, & \text{if $MP$ is infinite}\\
  \forall \component. ~ \contour(\component) = \HIGHSEC \rightarrow m_0(\component) = m_f(\component), & \text{otherwise} \\
\end{array}
\right .
\]  
\leo{TODO: DISCUSS: Figure out notation for first/last machine state in a trace}

@@

\definition{Transition}

Given a trace $MP$, a call map $\callmap$ and a code map $\codemap$,
an $n-${\em transition} to a callee $f$ is a pair of machine-policy
state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ in the trace
such that:
\begin{itemize}
\item one state pair steps to the other: 
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstoobs{\obs}_P (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

\definition{Stack Integrity}

Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack integrity} with respect to $\callmap$ and
$\codemap$ if, for every initial machine-policy state pair $(\mach_0,
\pol_0)$ and its induced trace $MP$, and every $n$-transition
$(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee $f$ in $MP$,
the prefix $MP_{pre}$ of $MP$ from $(\mach_e, \pol_e)$ until the first
return corresponding to $\mach_c$ (if any) satisfies trace integrity
with respect to the contour at the call:
%
$$\forall MP_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
MP_{pre} ~ | ~ \ret{\mach_c} \rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, f, n)~MP_{pre}$$

@@

\definition{Variations}

We say two machine states $\mach$ and $\mach'$ are {\em variations} of one
another given a contour $\contour$ if they agree on low
confidentiality data:
%
\[
\mach \approx_\contour \mach' \triangleq \forall \component .
\contour(\component) = \LOWSEC \rightarrow \mach(\component) =
\mach'(\component)
\]
%
Then, the trace version of confidentiality operates on two traces: the
``original'' one $MP \in \MPOTRACE$ that corresponds to a callee $f$
and a ``variant'' one $M \in \MTRACE$ that would corresponding to $f$
if it started from a variant initial machine state.

\definition{Trace Confidentiality}

\leo{Add info for ``valid return'':}
We will say two traces $MP$ and $M$ satisfy {\em trace
  confidentiality} with respect to $\contour$ if:
\begin{itemize}
\item If $MP$ is finite and its final state $\mach_r$ is a valid
  return, then $M$ is also finite with some final state $\mach_r'$ and
  any changes from the initial states have changed in the same way:
$$\forall \component. ~ \mach_e(\component) \not = \mach_r(\component)
  \vee \mach_e'(\component) \not = \mach_r'(\component) \rightarrow
  \mach_r(\component) = \mach_r'(\component)$$
  In addittion their observations must be equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$
\item If $MP$ is infinite, then $M$ is also infinite and their
  observations are equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$  
\item If the $MP$ ends prematurely with a policy fault, then
  we require that its observations are a prefix of those of $M$:
  $$\pi_o(MP) \lesssim \pi_o(M)$$
\end{itemize}

@@

\sna{Version for stepping from a state}
\definition{Confidential Execution}

  Stack confidentiality, below, is a property of a system that, from a call to
  a return, each trace obeys a local confidentiality property,
  {\it confidential execution}.

@@

\definition{Stack Confidentiality}

Let $\callmap$ be a call map and $\codemap$ a code map.
\rb{Could we find better symbols for the maps?}
We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $MP$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $MP$, the prefix $MP_{pre}$ of $MP$ from $(\mach_e, \pol_e)$
until the first return corresponding to $\mach_c$ (if any) satisfies
trace integrity with respect to every similarly prefixed machine trace
of every variation $\mach_e'$ with the contour at the call:
$$\forall MP_{pre} ~ M_{pre}. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P MP_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow M_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ MP_{pre} ~ M_{pre}$$

@@

\definition{Control Separation}

A system enjoys {\em control separation} with regard to a code map
\(\codemap\), a call map \(\callmap\), and a return map \(\retmap\) if
for any initial state \(\mach_0\) and any adjacent pair of states
\(\mach_1\) and \(\mach_2\) in the induced trace from
\(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
\(\codemap(\mach_1(\PCname)) \not = \codemap(\mach_2)\), then either
\(\callmap(\mach_1(\PCname)) = n\) for some \(n\), or
\(\retmap(\mach_1)\).

\definition{Entry Integrity}

A system enjoys {\em entry integrity} with regard to a call map
\(\callmap\) and entry map \(\entmap\) if for any initial state
\(\mach_0\) and any adjacent pair of states \(\mach_c\) and
\(\mach_e\) in the induced trace from
\(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
\(\callmap(\mach_c(\PCname)) = n\) then \(\entmap(\mach_e)\).

\definition{Return Integrity}

Return integrity captures the expected behavior of marked returns with
regard to their call points. We begin by defining a coinductive
relation \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT_1
\MPT_2\). Given a call map \(\callmap\) and return map \(\retmap\),
\(\MPT\) is related to \(\MPT'\) if \(\MPT'\) is a suffix of \(\MPT\)
whose head is the first unmatched return in \(\MPT\). So if \(\MPT\)
starts with a return, it is related to itself:

@@

\definition{Well Bracketed Control Flow}

The above properties are somewhat orthogonal, but together they
capture a standard notion of control flow for a stack: functions keep
their code separate outside of calls and returns, calls respect
explicit entry points, and returns respect implicit entry points
corresponding to their call.  A system that enjoys them with regard to
a code, a call, a return, and an entry map is said to enjoy {\em well
  bracketed control flow} with regard to those maps.

@@

    \definition{Observable Trace Integrity}

      Suppose a function \(f\) calls another function \(g\) with contour
      \(\contour\). If \(g\) alters an address below its stack frame, where
      \(\contour\) is \(\HIGHSEC\), the trace from the entry point to the
      return will not enjoy Trace Integrity. But if \(f\) immediately
      overwrites the overwritten location, the illegal write can be safely
      ignored, as it will never affect the behavior of the program.
      {\em Observable trace integrity} captures this intuition by guaranteeing
      that the final state, instead of being identical to the initial one,
      has the same behavior as it would if the writes had not occurred.

      Let \(\contour\) be a contour and \(\MPT\) be a finite \(\MPOTRACE\)
      whose initial machine state is \(\mach_e\). \(\MPT\) satisfies {\em trace
      integrity} with respect to \(\contour\) if the trace induced by its final
      state, \(\mpostate{\mach_r}{\pol}{\obs}\), is an observational prefix of
      that induced by an idealized state \(\mach_r'\) that agrees with
      \(\mach_r\) on all components marked \(\HIGHSEC\) in \(\contour\).
      Formally we define a rollback function, \(\mathit{roll}\), that takes
      two machine states and produces a third.
      %
      \[\mathit{roll}(\contour,\mach_e,\mach_r)(\component) =
      \begin{cases}
        \mach_c(\component) & \contour(\component) = (\HIGHINT,\_) \\
        \mach_r(\component) & \contour(\component) = (\LOWINT,\_) \\
      \end{cases}\]

      If \(\mach_e\) is an entry to a call with contour \(\contour\) and
      \(\mach_r\) its return, \(\mathit{roll}(\contour,\mach_e,\mach_r)\)
      agrees with \(\mach_e\) on every component the callee should not change,
      but with \(\mach_r\) on those components that it is permitted to change.
      So the observable behavior that follows is the idealized behavior to
      which we compare the trace from \(\mach_r\), which must prefix it (to
      account for premature halts due to policy violations.)
      %
      \[\begin{split}
        \text{\sc ObsInt}_\contour ~ \MPT \triangleq
          & \MPT = \mpostate{\mach_e}{\pol_e}{\obs_e} \dots
            \mpostate{\mach_r}{\pol_r}{\obs_r} \Rightarrow \\
        & \mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT' \Rightarrow \\
        & \mathit{roll}(\contour,\mach_e,\mach_r) \hookrightarrow \machT' \Rightarrow \\
        & \pi_o(\MPT') \lesssim_O \pi_o(\machT')
      \end{split}\]

    \definition{Observable Stack Integrity}

      A system enjoys {\em observable integrity} with regard to \(\callmap\)
      and  \(\codemap\) if for any initial state \(\mach_0\) and each
      transition with entry state \(\mpostate{\mach_e}{\pol_e}{\obs_e}\) and
      contour \(\contour\) in the induced trace from
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\), if
      \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_e}\),
      then \(\text{\sc ObsInt}_\contour ~ \MPT\).

    \definition{Observable Confidentiality}

      Observable confidentiality is concerned with whether high confidentiality
      data influences observable both behavior during and after a call. As with
      eager confidentiality, we will compare the behavior of the trace induced
      by a state to another induced by its variant. But if the original returns,
      before continuing, we must reset the variant to conform with the original
      state.

@@

    \definition{Observable Stack Safety}

      A system enjoys {\em observable stack safety} with regard to a call map
      and a code map if it enjoys both observable integrity and observable
      confidentiality with regard to them.

>>>>

But what {\em is} stack safety? A precise formal definition of stack
safety is lacking from the literature, with the notion only being
defined negatively: through examples of stack unsafety. Two classical
examples of stack unsafety appear in Figure~\ref{fig:stackunsafety}.
\leo{Goal: on the left, a bad read; on the right, a bad write.}
\leo{Do we also need an example of ROP/control flow for the new part?}
Recently, a \leo{inspiring/awesome/something good} work reasoned
about a stack safety enforcement mechanism using capabilities\leo{cite};
while impressive, stack safety was defined with respect to an abstract
machine that ``exhibits stack safety by construction''. Which begs
the question, what {\em is} the property that holds by construction?

\leo{StackTokens} provides some intuition towards answering that question,
by informally describing two components that comprise stack safety:
local state encapsulation and well-bracketed control flow. In this paper
we turn this intuition into two formal \leo{extensional} security properties,
that together form a formal definition of stack safety.

@@

While integrity and confidentiality are relatively standard security
properties, this setting provides an interesting additional challenge:
the notion of who the attacker shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be potentially proteced from {\em its} callees.  In
this paper we address this challenge by varying the observation power
of the attacker at call points, and demonstrate that our policy is
implementable by pre-existing monitoring mechanisms.

@@

Before we define stack safety, we need to first set the stage by
describing our machine model. Concretely, we have in mind a
conventional machine architecture with a standard (RISC-V) processor
extended with some kind of (static or dynamic, software- or
hardware-enforced) security monitor. However, our definition of stack
safety is generic: we will begin with an abstract interface to our
machine model and only make specific choices about details when we get
to the policy enforcement section~\ref{sec:micropolicy}.

@@

The basic building blocks of the machine are {\em values} and {\em
  addresses}. Both are drawn from some set of all possible words
$\WORDS$. We will denote words with $\word$.
%
Our machine states are comprised of {\em components}, that can be word
(denoting memory addresses) or registers (drawn from some set $\REGS$.
%
    \[\reg \in \REGS\]
    \[\component \in \COMPONENTS = \WORDS + \REGS \]
%
The registers must include two special purpose registers: the program
counter \PCname and the stack pointer \SP.
%
Formally, a machine state is just a map from components to values:
%
\[\mach \in \MACHS = \COMPONENTS \rightarrow \WORDS\]

@@

A trace over some type $A$ is a potentially infinite, nonempty
sequence of $A$s. We will mostly be concerned with sequences of
machines states, usually denoted $\machT$, and with sequences of
triples of (machine states, policy states, and observations), usually
denoted $\MPT$. To continue, we will require three generic operations
on traces: a ``trace-of'' operation to construct the potentially
infinite traced induced by a step relation; a ``split'', to break a
trace into two components based on a predicate; a ``join'', the
reverse of split; and a ``prefix'', as a shorthand to only keep the
first component of a split.

@@

\subsection{Program Structre}

@@

\definition{Trace Integrity}
\label{def:trace-integrity}
Let $\contour$ be a contour and $MP$ be a (potentially infinite)
$\MPOTRACE$. We will say $MP$ satisfies {\em trace integrity} with
respect to $\contour$ if its final state (if any) agrees with its
initial one on all components marked $\HIGHSEC$ in $\contour$:
%
\[
\mathit{int} ~ \contour ~ MP \triangleq
\left \{ \begin{array}{ll}
  \mathit{True}, & \text{if $MP$ is infinite}\\
  \forall \component. ~ \contour(\component) = \HIGHSEC \rightarrow m_0(\component) = m_f(\component), & \text{otherwise} \\
\end{array}
\right .
\]
\leo{TODO: DISCUSS: Figure out notation for first/last machine state in a trace}

@@

\definition{Transition}
Given a trace $MP$, a call map $\callmap$ and a code map $\codemap$,
an $n$-{\em transition} to a callee $f$ is a pair of machine-policy
state pairs $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ in the trace
such that:
\begin{itemize}
\item one state pair steps to the other: 
  $$\exists \obs. ~ (\mach_c, \pol_c) \stepstoobs{\obs}_P (\mach_e, \pol_e),$$
\item $\mach_c$ is a valid call with $n$ arguments:
  $$\callmap(\mach_c(\PCname)) = n,$$
\item and $\mach_e$ is an entry point for $f$:
  $$\codemap(\mach_e(\PCname)) = f.$$
\end{itemize}

\definition{Stack Integrity}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack integrity} with respect to $\callmap$ and
$\codemap$ if, for every initial machine-policy state pair $(\mach_0,
\pol_0)$ and its induced trace $MP$, and every $n$-transition
$(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee $f$ in $MP$,
the prefix $MP_{pre}$ of $MP$ from $(\mach_e, \pol_e)$ until the first
return corresponding to $\mach_c$ (if any) satisfies trace integrity
with respect to the contour at the call:
%
$$\forall MP_{pre}. ~ \mpstate{\mach_e}{\pol_e} \hookrightarrow_P
MP_{pre} ~ | ~ \ret{\mach_c} \rightarrow
\mathit{int}~\mathit{Cof}(\mach_c, f, n)~MP_{pre}$$

@@

\definition{Variations}
We say two machine states $\mach$ and $\mach'$ are {\em variations} of one
another given a contour $\contour$ if they agree on low
confidentiality data:
%
\[
\mach \approx_\contour \mach' \triangleq \forall \component .
\contour(\component) = \LOWSEC \rightarrow \mach(\component) =
\mach'(\component)
\]
%
Then, the trace version of confidentiality operates on two traces: the
``original'' one $MP \in \MPOTRACE$ that corresponds to a callee $f$
and a ``variant'' one $M \in \MTRACE$ that would corresponding to $f$
if it started from a variant initial machine state.

\definition{Trace Confidentiality}
\leo{Add info for ``valid return'':}
We will say two traces $MP$ and $M$ satisfy {\em trace
  confidentiality} with respect to $\contour$ if:
\begin{itemize}
\item If $MP$ is finite and its final state $\mach_r$ is a valid
  return, then $M$ is also finite with some final state $\mach_r'$ and
  any changes from the initial states have changed in the same way:
$$\forall \component. ~ \mach_e(\component) \not = \mach_r(\component)
  \vee \mach_e'(\component) \not = \mach_r'(\component) \rightarrow
  \mach_r(\component) = \mach_r'(\component)$$
  In addittion their observations must be equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$
\item If $MP$ is infinite, then $M$ is also infinite and their
  observations are equivalent:
  $$\pi_o(MP) \eqsim \pi_o(M)$$  
\item If the $MP$ ends prematurely with a policy fault, then
  we require that its observations are a prefix of those of $M$:
  $$\pi_o(MP) \lesssim \pi_o(M)$$
\end{itemize}

@@

\sna{Version for stepping from a state}
\definition{Confidential Execution}
  Stack confidentiality, below, is a property of a system that, from a call to
  a return, each trace obeys a local confidentiality property,
  {\it confidential execution}.

@@

\definition{Stack Confidentiality}
Let $\callmap$ be a call map and $\codemap$ a code map. We say that a
system satisfies {\em stack confidentiality} with respect to
$\callmap$ and $\codemap$ if, for every initial machine-policy state
pair $(\mach_0, \pol_0)$ and its induced trace $MP$, and every
$n$-transition $(\mach_c, \pol_c)$ and $(\mach_e, \pol_e)$ to a callee
$f$ in $MP$, the prefix $MP_{pre}$ of $MP$ from $(\mach_e, \pol_e)$
until the first return corresponding to $\mach_c$ (if any) satisfies
trace integrity with respect to every similarly prefixed machine trace
of every variation $\mach_e'$ with the contour at the call:
$$\forall MP_{pre} ~ M_{pre}. ~
\mpstate{\mach_e}{\pol_e} \hookrightarrow_P MP_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\forall \mach_e'. ~ \mach_e \approx_{\mathit{Cof}(\mach_c, f, n)} \mach_e' \wedge
\mach_e' \hookrightarrow M_{pre} ~ | ~ \ret{\mach_c} \rightarrow$$
$$\mathit{conf}~\mathit{Cof}(\mach_c, f, n) ~ MP_{pre} ~ M_{pre}$$

@@

\definition{Control Separation}
A system enjoys {\em control separation} with regard to a code map
\(\codemap\), a call map \(\callmap\), and a return map \(\retmap\) if
for any initial state \(\mach_0\) and any adjacent pair of states
\(\mach_1\) and \(\mach_2\) in the induced trace from
\(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
\(\codemap(\mach_1(\PCname)) \not = \codemap(\mach_2)\), then either
\(\callmap(\mach_1(\PCname)) = n\) for some \(n\), or
\(\retmap(\mach_1)\).

\definition{Entry Integrity}
A system enjoys {\em entry integrity} with regard to a call map
\(\callmap\) and entry map \(\entmap\) if for any initial state
\(\mach_0\) and any adjacent pair of states \(\mach_c\) and
\(\mach_e\) in the induced trace from
\(\mpstate{\mach_0}{\pinit(\mach_0)}\), if
\(\callmap(\mach_c(\PCname)) = n\) then \(\entmap(\mach_e)\).

\definition{Return Integrity}
Return integrity captures the expected behavior of marked returns with
regard to their call points. We begin by defining a coinductive
relation \(\mathit{Unmatched}\ \callmap\ \retmap\ \MPT_1
\MPT_2\). Given a call map \(\callmap\) and return map \(\retmap\),
\(\MPT\) is related to \(\MPT'\) if \(\MPT'\) is a suffix of \(\MPT\)
whose head is the first unmatched return in \(\MPT\). So if \(\MPT\)
starts with a return, it is related to itself:

@@

\definition{Well Bracketed Control Flow}
The above properties are somewhat orthogonal, but together they
capture a standard notion of control flow for a stack: functions keep
their code separate outside of calls and returns, calls respect
explicit entry points, and returns respect implicit entry points
corresponding to their call.  A system that enjoys them with regard to
a code, a call, a return, and an entry map is said to enjoy {\em well
  bracketed control flow} with regard to those maps.

@@

    \definition{Observable Integrity}
      Observable integrity weakens eager integrity by allowing a returned state
      to differ from its call state at high integrity components, provided the
      observable behavior of the induced trace from the return matches that of
      an idealized state whose high integrity components do match the call
      state.

      Given a contour, a call state, and a returned state, we define a
      ``rollback'' function \(\mathit{roll} : \CONTOURS \times \MACHS \times
      \MACHS \rightarrow \MACHS\). The rollback returns a state that matches
      the call state on those components that are high integrity in its
      contour, and matches the return state on low integrity components:
      \[\mathit{roll}(\contour,\mach_c,\mach_r)(\component) =
      \begin{cases}
        \mach_c(\component) & \contour(\component) = (\HIGHINT,\_) \\
        \mach_r(\component) & \contour(\component) = (\LOWINT,\_) \\
      \end{cases}\]

      Intuitively, the result of a rollback is an idealized state that
      reflects changes to accessible components, but ignores the callee's
      interference with the caller's data. Then the observable behavior of the
      resulting trace is the standard to which we expect the real trace to
      conform.

      A system enjoys observable integrity with regard to \(\callmap\) and 
      \(\codemap\) if for any initial state \(\mach_0\) and each adjacent pair
      of a call state \(\mach_c\) and a state \(\mach_e\) with policy state
      \(\pol_e\) in the trace induced by
      \(\mpstate{\mach_0}{\mathit{pinit}(\mach_0)}\) where
      \(\callmap(\mach_c) = n\) and \(\codemap(\mach_e) = \funid\),
      if \(\mpstate{\mach_e}{\pol_e} \hookrightarrow \MPT | \ret{\mach_c}\)
      with the return state \(\mach_r\) at the end of \(\MPT\), then the
      following holds.

      Let \(\contour = \mathit{Cof}(\mach_c,\funid,n)\) describe the security
      levels of the call and
      \(\mach_r' = \mathit{roll}(\contour,\mach_e,\mach_r)\). The induced
      traces \(\mpstate{\mach_r}{\pol_r} \hookrightarrow \MPT\) and
      \(\mach_r' \hookrightarrow \machT'\) must be equivalent up to
      possible policy failure: \(\MPT \sim_P \machT'\).

    \definition{Observable Confidentiality}
      Observable confidentiality is concerned with whether high confidentiality
      data influences observable both behavior during and after a call. As with
      eager confidentiality, we will compare the behavior of the trace induced
      by a state to another induced by its variant. But if the original returns,
      before continuing, we must reset the variant to conform with the original
      state.

@@

    \definition{Observable Stack Safety}
      A system enjoys {\em observable stack safety} with regard to a call map
      and a code map if it enjoys both observable integrity and observable
      confidentiality with regard to them.
